### 2016-02-01 ch05-initvals/InitialValuesPaper.tex
Include initvals review letter (prelim!)
Include review letter from initial values paper
Most of the review letter should go in the future.
Anyhow, at least the figures are already there, so we can add them
to the text.
Table with different stress test cases

\begin{equation}\label{eq:selectBest}
  \model{best} = 
    \Arg_{\hat{G}} 
    \min 
    \left\{ 
      V(\model{exist}),
      V(\model{trunc}),
      V(\model{RFIR})
    \right\}
\end{equation}
where $V(\hat{G})$ corresponds to the cost function in equation \eqref{eq:MLEcf} in the parametric estimates of $\hat{G}$.
This is also the approach followed in~\citep{FDIDENT} to combine different initial estimates.

@@

\begin{remark}
  In the simulations (e.g. \figref{fig:single-sim}), a $60\unit{dB}$ difference between `good' and `bad' estimates was observed.
  Such a large gap is not observed in the measurements (\figref{fig:costMeasurements} and \tabref{tbl:costMeasurements}).
  Hence, defining a success rate based on a threshold tolerance would be very sensitive to the specific value of the threshold and hence unreliable.
  Instead, the statistical location and dispersion are inspected to assess the relative performance of each method.
  Practically, the median is used as a measure of location and the \gls{IQR} is used to inspect the spread as these are far more robust to outliers than e.g. the sample mean and variance.
  These measures also have an easy interpretation: the median ($50\%$ percentile) indicates the cost function value that $50\%$ of the repetitions attain.
  On the other hand, the \gls{IQR} ($25\%$ through $75\%$ percentile) contains  exactly half of the observations.
\end{remark}
\TODO{define IQR mathmatically}

@@

\subsubsection{Validation criterion}
To objectively assess the quality of an estimated model, a different criterion than the cost function is inspected.
To this end, the model is validated using the 2-norm (or distance) on the model error:
\begin{equation}
  \norm{\model{\bullet} - G_{\mathrm{VXI}}}
  \text{.}
  \label{eq:measurementCriterion}
\end{equation} 
This criterion indicates how well the obtained estimates $\model{\bullet}$ are able to describe the transfer function of the bandpass filter as observed in the validation measurement on the VXI.

@@

\section{Remark on Generality}
\label{se:Generality}
In the previous sections, the usefulness of smoothing techniques to obtain initial values has been illustrated on example systems.
Other systems, e.g. discrete-time low-pass, high-pass, band-pass and band-stop filters of tenth order generated by the \code{cheby1}, \code{cheby2}, \code{ellip} and \code{butter} commands in \MATLAB{} have also been tried.

No cases were observed where using the smoothing to obtain initial values worsens the obtained model quality when the candidate model with the lowest cost function value is used (as in \eqref{eq:selectBest}).
On the contrary, significant improvements were often achieved by including the initial values from the smoothed FRF and by combining different strategies.

The usefulness of particular initial estimates, e.g. $\model[init]{RFIR}$ is obviously linked to the appropriateness of the non-parametric smoother in the experimental conditions at hand.
However, it is beyond the scope of this paper to determine which particular smoother is optimal in some specific circumstance.

\TODO{figures from review letter}

@@

% \bibliographystyle{IEEEtran}
% \bibliography{InitEstBib}
% \end{document}

>>>>

\begin{equation}\label{eq:selectBest}
  \model{best} = 
    \Arg_{\hat{G}} 
    \min 
    \left\{ 
      V(\model{exist}),
      V(\model{trunc}),
      V(\model{RFIR})
    \right\}
\end{equation}
where $V(\hat{G})$ corresponds to the cost function in equation \eqref{eq:MLEcf} in the parametric estimates of $\hat{G}$.
This is similar to the approach followed in~\citep{FDIDENT} to combine different initial estimates.

@@

\begin{remark}
  In the simulations (e.g. \figref{fig:single-sim}), a $60\unit{dB}$ difference between `good' and `bad' estimates was observed.
  Such a large gap is not observed in the measurements (\figref{fig:costMeasurements} and \tabref{tbl:costMeasurements}).
  Hence, defining a success rate based on a threshold tolerance would be very sensitive to the specific value of the threshold and hence unreliable.
  Instead, the statistical location and dispersion are inspected to assess the relative performance of each method.
  Practically, the median is used as a measure of location and the \gls{IQR} is used to inspect the spread as these are far more robust to outliers than e.g. the sample mean and variance.
  These measures also have an easy interpretation: the median ($50\%$ percentile) indicates the cost function value that $50\%$ of the repetitions attain.
  On the other hand, the \gls{IQR} ($25\%$ through $75\%$ percentile) contains  exactly half of the observations.
\end{remark}

@@

\subsubsection{Validation criterion}
To objectively assess the quality of an estimated model, a different criterion than the cost function is inspected.
To this end, the model is validated using the 2-norm (or distance) on the model error:
\begin{equation}
  \validationDistance{\bullet} 
  \isdef 
  \norm{\model{\bullet} - G_{\mathrm{VXI}}}
  \text{.}
  \label{eq:measurementCriterion}
\end{equation} 
This criterion indicates how well the obtained estimates $\model{\bullet}$ are able to describe the transfer function of the bandpass filter as observed in the validation measurement on the VXI.

@@

\section{Remark on Generality}
\label{se:Generality}
In the previous sections, the usability of the smoothers to produce initial values has been studied on very specific examples.
In this section, an attempt will be made to illustrate the usefulness of these smoothers for the generation of starting values for other systems.
However, due to the intricate relationship between the attraction regions in the cost function, the location of the actual system poles, the \gls{SNR} level and the choice of a particular excitation signal, we think it is intractable to construct rigid bounds on where the smoothers produce effective starting values.

\subsection{Limitations of the smoothers}
On the one hand, an obvious limitation to the presented initialization techniques is that they share the limitations of the smoothing techniques: if the non-parametric estimate is a worse representation than the raw data (e.g. heavily biased), it is very unlikely that the initial estimate will outperform the existing estimates.
However, it is beyond the scope of this chapter to determine formally which particular smoother is optimal in some specific experimental circumstances.

In particular for RFIR, a simulation study in~\cite{Chen2013} suggests that RFIR handles systems with model orders up to at least $30$, even for small datasets $N\leq 500$.
For LPM (with or without time-truncation), no comparable studies are available to our knowledge, but the LPM itself has been used successfully in diverse practical applications.

\subsection{Stress test of the smoothers}
To test the effectiveness of the initial estimates obtained from these particular smoothers, an extra set of $n_{\mathrm{MC}} = 100$ Monte Carlo simulations were performed.
In particular, we used
\begin{itemize}
  \item low-pass, high-pass, band-pass and band-stop 
  \item Chebyshev Type I, Chebyshev Type II, Elliptical and Butterworth
\end{itemize}
discrete-time filters (see \figref{fig:bodeplots}) of tenth degree generated by the MATLAB functions \texttt{cheby1}, \texttt{cheby2}, \texttt{ellip} and \texttt{butter} and an SNR of $20 \unit{dB}$ and $N=1024$ measured samples.
The band-pass and band-stop filters actually have a model order of 20.

\TODO{add table with different transfer functions, generation code, etc. for stress test}

The input excitation and the disturbing output noise were both white and Gaussian.

\begin{figure}[p]
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \centering
  \ref{leg:init:stress:bodes}
  \input{\thisDir/fig/bodeplots.tikz}
  \caption[Bode plots of the stress test filters.]{Bode plots of the tested filters~\legref{leg:bode:true} in the stress test. 
  For each filter, two of the parametric estimates $\model{\bullet}$ are shown per method.
  Top to bottom: Chebyshev I, Chebyshev II, Elliptical and Butterworth characteristic.
  Left to right: low-pass, band-pass, high-pass and band-stop.
  }
  \label{fig:bodeplots}
\end{figure}

\begin{figure}[p]
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \centering
  \ref{leg:distances}
  \input{\thisDir/fig/distances.tikz}
  \caption[Empirical \glsentrytext{CDF} of $\validationDistance{\bullet}$ in the stress test.]{Empirical cumulative distribution function of the validation distance $D_{\bullet} = \norm{\model{\bullet} - G_0}$ for the different tested systems (different numbered plots) and the different initial values (colors).
  Note that since $\norm{G_0}=1$ is chosen, $D_{\bullet}$ immediately indicates the relative RMS error of the estimates.
  }
  \label{fig:distancesStress}
\end{figure}

\begin{table}[p]
  \centering
% \input{\thisDir/table2.tex}
  \caption{Overview of the test cases for the initialization stress test.}
\begin{tabular}{crlrrrr}
\toprule
\textsc{Case}   &  \multicolumn{2}{c}{\textsc{Filter}}   &  $\true{\eta}$  &  $\eta_{\mathrm{exist}}$   &  $\eta_{\mathrm{RFIR}}$  &  $\eta_{\mathrm{best}}$ \\
\midrule
1  &  {Chebyshev I}  &  low-pass   &  0  &  0  &  0  &  0\\
2  &  {Chebyshev I}  &  band-pass   &  0  &  0  &  0  &  0\\
3  &  {Chebyshev I}  &  high-pass   &  0  &  0  &  0  &  0\\
4  &  {Chebyshev I}  &  band-stop   &  0  &  0  &  0  &  0\\
5  &  {Chebyshev II}   &  low-pass   &  0  &  0  &  0  &  0\\
6  &  {Chebyshev II}   &  band-pass   &  0  &  0  &  0  &  0\\
7  &  {Chebyshev II}   &  high-pass   &  0  &  0  &  0  &  0\\
8  &  {Chebyshev II}   &  band-stop   &  0  &  0  &  0  &  0\\
9  &  Elliptical   &  low-pass   &  0  &  0  &  0  &  0\\
10   &  Elliptical   &  band-pass   &  0  &  0  &  0  &  0\\
11   &  Elliptical   &  high-pass   &  0  &  0  &  0  &  0\\
12   &  Elliptical   &  band-stop   &  0  &  0  &  0  &  0\\
13   &  Butterworth  &  low-pass   &  0  &  0  &  0  &  0\\
14   &  Butterworth  &  band-pass   &  0  &  0  &  0  &  0\\
15   &  Butterworth  &  high-pass   &  0  &  0  &  0  &  0\\
16   &  Butterworth  &  band-stop   &  0  &  0  &  0  &  0\\
\bottomrule
\end{tabular}
\label{tbl:init:stresstest}
\end{table}

\subsection{Observations}
The transfer functions are shown in \figref{fig:bodeplots} while the empirical cumulative validation distance is shown in \figref{fig:distancesStress}.

A few remarks regarding these results are appropriate.
\begin{itemize}
  \item In many of the tested situations (cases 1,3,13-16), all methods yield a good model quality.
  \item In some situations (cases 8, 10, 12), the model quality is generally poor. 
  The fact that for cases 8 and 12, the `ideal' starting value \model{0} also provides poor models means the data is not informative enough to reasonably fit a good model.
  \item In all cases except 8, 10 and 12, the RFIR performed as well or better than the existing methods.
  \item In case 10, the model quality of the RFIR is slightly worse than the already poor existing techniques.
  This is a underlying limitation of the RFIR used: $n_g=200$ taps was used, however the true impulse response has not decayed significantly in that interval.
  Essentially, the particular RFIR used introduces a significant bias in the non-parametric description of the filter and hence the obtained initial value is unreliable.
  \item The RFIR performs (significantly) better than the existing methods in various cases (4-7, 9, 11).
  \item Since the `best' method \legref{leg:dist:modelBest} yields better models more often than a single method, e.g. in cases 2, 4 and 6, this illustrates that combining initialization schemes improves the model quality.
  Particularly, case 2 implies that \model{best} contains initial estimates of all different techniques.
  \item For all of the tested systems (except possibly for case 2), the truncated LPM is not advisable over the existing methods.
\end{itemize}

In general, one can see from these simulations that \gls{RFIR} either performs as well as (or even better than) the existing techniques when a good estimate is obtained.
There are no cases where using the smoothing to obtain initial values worsens the obtained model quality when the candidate model with the lowest cost function value is used (as in \eqref{eq:selectBest}).
On the contrary, significant improvements were often achieved by including the initial values from the smoothed FRF and by combining different strategies.

@@

### 2016-02-01 ch05-initvals/letter.inc.tex
Table with different stress test cases

\reviewer{Reviewer \#2 (Remarks for the Author):}
\begin{quote}
The authors propose two smoothing techniques, which improve the initial estimates for transfer function identification. Figure 2 and section VI are appreciated.

Comments:

1. Please treat carefully the optimization problems. Just presenting the cost functions is not enough.

3. Which are the optimization algorithms? Clear steps must be provided. 
\end{quote}
Note that the minimization of the cost function (5) in the paper has been extensively studied in the literature (e.g. \cite[Section 9.11]{Pintelon2001} which has been referenced in the manuscript).
We have used the well-known Levenberg-Marquardt optimization algorithm to perform the non-convex optimization.
This information has also been added to the paper.

\begin{quote}
2. Do your smoothing techniques guarantee and/or keep the minimum? 
\end{quote}
The cost function involving the smoothed estimate is different from the cost function with the raw data. 
Obviously, in that case the minimum is expected to be shifted.
However, the result from this cost function is used as an \emph{initial} estimate for the cost function with the raw data. 
In the end, only the cost function with the raw data is retained.
The initial estimate does \emph{not} change the minimum of a cost function.

\begin{quote}
4. The transparency of the paper is suffering because the authors do not present how the theoretical results from sections II and III are applied in section IV.

5. The same comment is also applied for section V, i.e., low transparency. 
\end{quote}

The theoretical considerations in sections II and III are applied in section IV.
In section III, the initial estimation procedures are enumerated, and a distinct notation for each of them is given:
\begin{itemize}
  \item use of the true parameters: $\model{0}$,
  \item use of existing techniques: $\model{exist}$,
  \item use of the LPM with truncation: $\model{trunc}$,
  \item use of the RFIR: $\model{RFIR}$.
\end{itemize}
Then, the results of the latter three initialization techniques are compared to the results with $\model{0}$ in Section IV (simulations) and Section V (measurements).

\begin{quote}
6. I am not sure if section IV is actually necessary. You may drop it out. 
\end{quote}

The presence of section IV is crucial for the article, and will not be skipped, for the following reason. 
The goal of the article is to demonstrate that the use of smoothing techniques increases the success rate the minimization of the ML cost function. 
While Sections II and III introduce the methods used, Section IV actually \emph{does} the demonstration of the improvement. 
It is important to include the simulation results, because these allow to make Monte Carlo simulations at various SNR values, to obtain statistically meaningful results. 
It would be much more difficult to apply a Monte Carlo method to the measurements, since a huge number of experiments must be performed, with different experimental conditions (SNR), on a variety of different systems.

\begin{quote}
2) It is unclear how generalizable the procedure introduced by Authors is, and what is its domain of applicability. Based on section IV Demonstration (simulated data), a reader may be convinced that RFIR is the absolute winner.

So, it comes as an unpleasant surprise in section V Experimental Results to learn that RFIR only wins in $50\%$ of cases (Table I). The natural question of ``why so different'' is never discussed. It seems that a lack of ground truth in a real experiment is correctly addressed by using a response from an almost noiseless system (60dB, p.18). Could it be that in simulation two low-pass filters were investigated (each with $n_{\theta} = 5$ parameters, p.13), while in experiment pass-band filter was tested with $n_{\theta} = 9$ adjustable parameters? Having the same system tested in simulations and in experiment could partially answer this question.

However, the results in Table I do not necessarily nullify a usefulness of the RFIR as a starting point. It may be that in the cases when $\model{RFIR}$ is not the best estimate, a difference between $\model{best}$ and $\model{RFIR}$ is acceptably small. If for cases when $\model{best} = \model{RFIR}$ is much better than the second best estimate $G_{2nd}$, then it makes sense to always use RFIR, as a penalty for wrong choice would be mild.

\end{quote}

The fact that ‘only’ $50\%$ of the RFIR estimates turn out to be the best estimates does not mean that the remaining $50\%$ from RFIR are bad estimates. 
It simply means that, for the remaining $50\%$, the other methods (trunc and exist) happened to give a slightly smaller cost function. 
Since Table I is misleading, we have decided to remove it from the paper.

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/fig/overview-cost-val.tikz}
  \caption{Cost function $V(\model{\bullet})$ and validation distance of the model estimated in each repetition of the measurement.
  The same data as in Fig.~10 and Fig.~11 of the paper is presented.
  Based on the cost function, $\model{RFIR}$~\legref{leg:RFIR} is not always the best estimate $\model{best}$~\legref{leg:best}.
  Especially in the validation plot (bottom), $\model{RFIR}$ performs (almost) as well or even better than $\model{exist}$~\legref{leg:exist} and $\model{trunc}$~\legref{leg:trunc}.
  Both latter methods often produce models that perform poorly compared to $\| G_{VXI} \|$~\legref{leg:reference} and $\model{VXI}$~\legref{leg:VXI}.
  This means that in our limited experimental study, the performance degradation of choosing RFIR to produce initial values over the studied alternatives is negligible.}
  \label{fig:overview}
\end{figure}

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.75\columnwidth}
  \setlength{\figureheight}{0.60\figurewidth}
  \input{\thisDir/fig/special-histogram.tikz}
  \caption{
  Performance degradation/enhancement ($X_{\bullet}-X_{\mathrm{best}}$) for choosing a given method $\bullet$ instead of the `best' method for the measurement example in the paper.
  In red/orange the positive values ($X_{\bullet} > X_{\mathrm{best}}$), the performance degradation for using $\model{\bullet}$ over $\model{best}$ is shown.
  The negative values ($X_{\bullet} < X_{\mathrm{best}}$), i.e. the performance enhancement (for using $\model{\bullet}$ instead of $\model{best}$) is shown in green/blue.
  Zero values (i.e. $X_{\bullet} = X_{\mathrm{best}}$) are not shown, hence the data shows when method $\bullet$ is \emph{not} selected as the `best' method.
  The dashed lines are the minimum, median and maximum of $X_{\bullet}$ to give a sense of scale.
  The performance degradation of choosing $\model{RFIR}$ instead of $\model{best}$ is smaller than the corresponding performance degradation for the other methods.
  The performance enhancement from choosing $\model{RFIR}$ over $\model{best}$, is almost on par with the corresponding performance degradation (i.e. there is little to gain \emph{or} lose from choosing $\model{RFIR}$ over $\model{best}$).
  For $\model{trunc}$ and $\model{exist}$, there is much less performance to gain from picking those over $\model{best}$ and there is a lot more to lose.
  }
  \label{fig:histogram}
\end{figure}

@@

\begin{quote}
The abstract promises a better starting point for a minimization of a non-convex cost function. However, no effort is undertaken in the paper to show that improvement is expected ``in most cases'' (or, under which conditions). The boundaries between different domains of starting points leading to different local minima may be very complicated. In fact, the higher the dimension of a search space is ($n_{\theta}$), the more likely it is that the boundaries are more complicated.

It is obvious that in some cases where subsets of starting points stretch over the boundaries, a particular strategy for selecting a starting point may lead to improvement. However, the paper doesn't explain why this should happen ``in most cases''. A reader would gain more confidence in a robustness of the introduced method if its boundary of applicability were clearly spelled out (for example: the method applicable to filters of order less than ... based on extensive testing). 
\end{quote}

We agree that the complicated boundaries between attraction regions of the different local optima of a cost function makes this a hard problem.
Moreover, the intricate relationship between the actual pole locations, signal SNR, choice of excitation signal, \ldots and shape of the cost function makes that determining clear boundaries on the usability of a starting value seems intractable to us.

On the one hand, an obvious limitation to the presented initialization techniques is that they share the limitations of the smoothing techniques: if the non-parametric estimate is a worse representation than the raw data (e.g. heavily biased), it is very unlikely that the initial estimate will outperform the existing estimates.
In particular for RFIR, a simulation study in~\cite{Chen2013} suggests that RFIR handles systems with model orders up to at least $30$, even for small datasets $N\leq 500$.
For LPM (with or without time-truncation), no comparable studies are available to our knowledge, but the LPM itself has been used successfully in diverse practical applications.

For the parametric estimates, we ran some additional simulations to verify the usability of the proposed initial values.
In particular, we used
\begin{itemize}
  \item low-pass, high-pass, band-pass and band-stop 
  \item Chebyshev Type I, Chebyshev Type II, Elliptical and Butterworth
\end{itemize}
discrete-time filters (see \figref{fig:bodeplots}) of tenth degree generated by the MATLAB functions \texttt{cheby1}, \texttt{cheby2}, \texttt{ellip} and \texttt{butter} and an SNR of $20 \unit{dB}$ and $N=1024$ measured samples.
Note: the band-pass and band-stop filters actually have a model order of 20.

The input excitation and the disturbing output noise were both white and Gaussian.
The results of a Monte Carlo simulation consisting of $100$ runs (as described above) have been summarized qualitatively in the paper (due to limited space) and are discussed below in more detail.

\TODO{add table with different transfer functions, generation code, etc. for stress test}

\begin{figure}[p]
  \setlength{\figurewidth}{0.75\columnwidth}
  \setlength{\figureheight}{0.6\figurewidth}
  \centering
  %\ref{legBodes}
  \input{\thisDir/fig/bodeplots.tikz}
  \caption{Bode plots of the tested filters~\legref{leg:bode:true}. Top to bottom: Chebyshev I, Chebyshev II, Elliptical and Butterworth characteristic.
  Left to right: low-pass, band-pass, high-pass and band-stop.
  For each filter, two of the parametric estimates $\model{\bullet}$ are shown per method.
  }
  \label{fig:bodeplots}
\end{figure}

\begin{figure}[p]
  \setlength{\figurewidth}{0.75\columnwidth}
  \setlength{\figureheight}{0.6\figurewidth}
  \centering
  \input{\thisDir/fig/distances.tikz}
  \caption{Empirical cumulative distribution function of the validation distance $D_{\bullet} = \norm{\model{\bullet} - G_0}$ for the different tested systems (different numbered plots) and the different initial values (colors).
  Note that since $\norm{G_0}=1$ is chosen, $D_{\bullet}$ immediately indicates the relative RMS error of the estimates.
  }
  \label{fig:distancesStress}
\end{figure}

The transfer functions are shown in \figref{fig:bodeplots} while the empirical cumulative validation distance is shown in \figref{fig:distancesStress}.

Our general conclusion from these simulations is that RFIR performs as well (or a lot better) than the existing techniques when good models are observed.

{\footnotesize
A few additional remarks are appropriate with respect to these results:
\begin{itemize}
  \item In many of the tested situations (subplots 1,3,13-16), all methods yield a good model quality.
  \item In some situations (subplots 8, 10, 12), the model quality is generally poor. 
  The fact that for subplots 8 and 12, the `ideal' starting value \model{0} also provides poor models means the data is not informative enough to reasonably fit a good model.
  \item In all cases except 8, 10 and 12, the RFIR performed as well or better than the existing methods.
  \item In subplot 10, the model quality of the RFIR is slightly worse than the already poor existing techniques.
  This is a underlying limitation of the RFIR used: $n_g=200$ taps was used, however the true impulse response has not decayed significantly in that interval.
  Essentially, the particular RFIR used introduces a significant bias in the non-parametric description of the filter and hence the obtained initial value is unreliable.
  \item The RFIR performs (significantly) better than the existing methods in various cases (subplot 4-7, 9, 11).
  \item Since the `best' method \legref{leg:dist:modelBest} yields better models more often than a single method, e.g. in subplots 2, 4 and 6, this illustrates that combining initialization schemes improves the model quality.
  Particularly, subplot 2 implies that \model{best} contains initial estimates of all different techniques.
  \item For all of the tested systems (except perhaps subplot 2), the truncated LPM is not advisable over the existing methods.
\end{itemize}
}

>>>>

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/fig/overview-cost-val.tikz}
  \caption[$\costFunc{\bullet}$ and $\validationDistance{\bullet}$ for each repeated measurement.]{Cost function $V(\model{\bullet})$ and validation distance of the model estimated in each repetition of the measurement.
  Based on the cost function, $\model{RFIR}$~\legref{leg:RFIR} is not always the best estimate $\model{best}$~\legref{leg:best}.
  Especially in the validation plot (bottom), $\model{RFIR}$ performs (almost) as well or even better than $\model{exist}$~\legref{leg:exist} and $\model{trunc}$~\legref{leg:trunc}.
  Both latter methods often produce models that perform poorly compared to $\| G_{VXI} \|$~\legref{leg:reference} and $\model{VXI}$~\legref{leg:VXI}.
  This means that in our limited experimental study, the performance degradation of choosing RFIR to produce initial values over the studied alternatives is negligible.}
  \label{fig:overview}
\end{figure}

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.75\columnwidth}
  \setlength{\figureheight}{0.60\figurewidth}
  \input{\thisDir/fig/special-histogram.tikz}
  \caption[Performance degradation/enhancement for selecting the second best model.]{
  Performance degradation/enhancement ($X_{\bullet}-X_{\mathrm{best}}$) for choosing a given method $\bullet$ instead of the `best' method for the measurement example in the paper.
  In red/orange the positive values ($X_{\bullet} > X_{\mathrm{best}}$), the performance degradation for using $\model{\bullet}$ over $\model{best}$ is shown.
  The negative values ($X_{\bullet} < X_{\mathrm{best}}$), i.e. the performance enhancement (for using $\model{\bullet}$ instead of $\model{best}$) is shown in green/blue.
  Zero values (i.e. $X_{\bullet} = X_{\mathrm{best}}$) are not shown, hence the data shows when method $\bullet$ is \emph{not} selected as the `best' method.
  The dashed lines are the minimum, median and maximum of $X_{\bullet}$ to give a sense of scale.
  The performance degradation of choosing $\model{RFIR}$ instead of $\model{best}$ is smaller than the corresponding performance degradation for the other methods.
  The performance enhancement from choosing $\model{RFIR}$ over $\model{best}$, is almost on par with the corresponding performance degradation (i.e. there is little to gain \emph{or} lose from choosing $\model{RFIR}$ over $\model{best}$).
  For $\model{trunc}$ and $\model{exist}$, there is much less performance to gain from picking those over $\model{best}$ and there is a lot more to lose.
  }
  \label{fig:histogram}
\end{figure}

@@
